Titeln på avhandlingens språk

### 2022-08-29 model.tex
workng on model ;

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{./model_data/duration_vs_exectime.png}
    \caption{}\label{fig:timing:durvsetime}
\end{figure}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{\cref{fig:timing:durvsetime} shows how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021}}
\end{figure*}
